---
title: "Programming Background"
author: "Kaylee Frazier"
date: "9/14/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.path = "../images/")
```

```{```{r, echo = FALSE, eval = FALSE}
rmarkdown::render("2021-9-14-Programming-Background.Rmd", output_format = "github_document", output_dir = "C:\Users\kayle\OneDrive\Documents\ST558HW\kafrazi2.github.io\ _posts"), output_options = list(
  
)
}

## Thoughts on R vs. other languages

### I like using R because it is a very commonly used language, so it is easy to collaborate with other and get help through the internet when I am struggling with my code. I like all of the different packages that you can install in R that makes certain aspects of coding easier than in other languages.

### The other language that I am more comfortable with is SAS. I miss this language because I have worked with it for so long that I know all the basic functions and I understand what the errors mean more in this language. 

### I think R is a fairly easy language to learn compared to other languages I have worked with. It is very user-friendly. 

## R Markdown Output
```{r}
plot(iris)
```


